A Sample Mathematics Paper

### 2014-11-20 writeups/multilevel.tex

>>>>

\section{Multilevel model}

\begin{align}
&\text{goldstein}_i &&\sim N(\alpha^{countryyear}_{j[i]}, \sigma^2_{goldstein}) \\
&\alpha_j^{countryyear} &&\sim N(\beta_{k[j]}^{country} + \gamma \cdot \text{liec}_j + \Gamma X_j, \sigma_{\alpha}^2) \\
&\beta_k^{country} &&\sim N(\delta_{ethnic} \cdot \text{ethnic}_k, \sigma_\beta^2) 
\end{align}
